Constant-sized correlations are sufficient to robustly self-test maximally entangled states with unbounded dimension

### 2019-08-12 Draft/draft.tex
changes to section 3

The inspiration comes from 
Slofstra's seminal work~\cite{slofstra2017}, in which he
embeds a group with generators $x$ and $y$ satisfying the relation $xyx^{-1}=y^2$
into the solution group of a binary linear system game.  
We generalize the relation $xyx^{-1} = y^2$ and embed the 
following group
\begin{align}
    \Pg = \ip{u,o:uou^{-1} = o^r},
\label{eq:pgroup}
\end{align}
for some $r \in \N$ into the solution group, denoted by $\Gamma$, of a binary linear system game, denoted by $\LS(r)$.
Since the steps to embed $\Pg$ into $\Gamma$ follows the procedure detailed in the proofs of Proposition~$33$, Lemma~$29$ and
Proposition $27$ of Ref.~\cite{slofstra2017}, 
we defer the formal statements of the embedding procedure till \cref{sec:embedding},
but sketch this procedure in \cref{sec:embed_idea}. 
In \cref{sec:gamma_def}, we define $\Gamma$ and introduce how to
construct $\LS(r)$ from $\Gamma$.
We also highlight a few operators from a finite-dimensional representation of $\Gamma$.
The representation will be used later to build the ideal strategy.

%----------------------------------------
\subsection{A sketch of the procedure
for constructing $\LS ( r )$}
\label{sec:embed_idea}
%----------------------------------------
The group $\Pg$ (\cref{eq:pgroup}) is first embedded into $\Pg_0$ (\cref{def:g0}), then $\Pg_1$ (\cref{def:g1}), and finally into the group $\Gamma$ (\cref{def:gamma}), which is the
solution group of $\LS ( r )$.  
Thus we obtain a chain of embeddings:
\begin{align}
\Pg \hookrightarrow \Pg_0 \hookrightarrow \Pg_1 \hookrightarrow
\Gamma.
\end{align}
The purposes of introducing each intermediate
group are explained below.

The group $\Pg_0 := \ip{S_0:R_0}$ is a 
conjugacy group, which is defined in \cref{def:spe_conj_grp}. 
The generators in $S_0$ are $a_i$ for $i=1 \dots r+5$.
The purpose of this step is to embed $\Pg$ into a group where all the
generators are of order-$2$, because
it is impossible to find a homomorphism from $\Pg$ to a solution group that maps $u$ or $o$, which can have arbitrary order, to a single generator. On the other hand, 
a homomorphism from $\Pg_0$ to a solution group can be easier to find.
The special generators of $\Pg_0$ are $a_1, a_2, a_3$ and $a_4$ because the product $a_1a_2$ behaves similarly as $o$
and the product $a_3a_4$ behaves similarly as $u$.
Moreover, the conjugacy relations in $R_0$ can be combined to recover the relation $uou^{-1} = o^r$ (see \cref{prop:g0}), so
a homomorphism: $\Pg \rightarrow\Pg_0$  that maps $o$ to $a_1a_2$ and $u$ to $a_3a_4$ is an embedding of $\Pg$ into $\Pg_0$
by Proposition $33$ of Ref.~\cite{slofstra2017}.
To better characterize the conjugacy relations in $R_0$, we introduce $C(r)$ defined in \cref{eq:cr}
of tuples $(i,j,k)$ such that $(i,j,k) \in C(r)$ if and only if $a_ia_ja_i = a_k$ is in $R_0$.

Next, we introduce group $\Pg_1 := \ip{S_1: R_1}$ where $S_0 \subset S_1$, which is a nice conjugacy group defined in \cref{def:nice_conj_grp}.
The special property of $R_1$ is that every relation in $R_0$ can be recovered from $R_1$.
Ensuring that every conjugacy relation is associating two commuting operators is the purpose of introducing $\Pg_1$. \carl{I think a reader would find that last statement unclear.}
\hfc{Maybe we just remove it?}
It makes the construction of a finite-dimension representation of $\Gamma$ from
a finite-dimension representation of $\Pg_1$ easier.
Specifically, in this step, we introduce generators $a_i, b_i, c_i, d_i \in S_1$
for each generator $a_i \in S_0$.
There is also a special generator $f_0 \in S_1$ such that
\begin{align*}
    a_i = b_ic_i = f_0d_i. 
\end{align*}
The relation $a_i = b_ic_i$ guarantees that $b_i$ commutes
with $c_i$.
The generators $b_i$ and $c_i$ are also related by a conjugacy relation
\begin{align*}
    c_i = f_0 b_i f_0. 
\end{align*}
For each $(i,j,k) \in C(r)$, 
$S_1$ contains an auxiliary generator $h_{jk}$, and
$R_1$ 
contains a conjugacy relation 
\begin{align*}
    d_ib_jd_i = c_k,
\end{align*}
and a linear relation
\begin{align*}
    h_{jk}b_jc_k = e.
\end{align*}
The introduction of $h_{jk}$ helps us to deduce that 
$b_j$ commutes with $c_k$.
Hence, every conjugacy relation in $R_1$ is either of the form
$f_0b_if_0 = c_i$ for $1 \leq i \leq r+5$, or
$d_ib_jd_i = c_k$ for $(i,j,k) \in C(r)$.
From the conjugacy relations in $R_1$, it can be proven that
\begin{align*}
    d_ic_jd_i = b_k \text{ for each } (i,j,k) \in C(r).
\end{align*}
Then we can expand $a_ia_ja_i$ by first substituting in $a_i = f_0 d_i$ and $a_j = b_jc_j$ and then repeatedly substituting in the conjugacy relations in $R_1$ and 
the conjugacy relations deduced above, so we can get
\begin{align*}
    a_ia_ja_i = f_0 d_i b_jc_j f_0 d_i
		= (f_0 d_i b_j d_i f_0)(f_0 d_i c_j d_i f_0) 
		= (f_0 c_k f_0)(f_0 b_k f_0) 
		= b_k c_k = a_k.
\end{align*}

A representation of $\Pg_1$ can also be built upon a representation of $\Pg_0$.
Suppose $\Psi_0$ is a representation of $\Pg_0$ on some Hilbert space $\calH$, then 
 a representation of $\Pg_1$, $\Psi_1$, on the Hilbert space $\C^2 \x \calH$ can
 be constructed such that
\begin{align*}
    &\Psi_1(a_i) = \1_{\C^2} \x \Psi_0(a_i).
\end{align*}
For more details of $\Psi_1$, we refer to \cref{sec:rep_gamma}.
Hence, a homomorphism $\phi: \Pg_0 \rightarrow \Pg_1$ that 
maps $a_i$ to $a_i$ is an embedding of $\Pg_0$ into $\Pg_1$
by Lemma $15$ of Ref.~\cite{slofstra2017}.

In the last step, we can construct $\Gamma:= \ip{S:R}$ with $S_1 \subset S$, in a way such that
$\Gamma$ only has linear relations, and the linear relations can be combined
to recover the conjugacy relations in $R_1$.
We demonstrate how relation $f_0 b_1 f_0 = c_1$ is embedded in
$6$ linear relations of $R$ as an example. 
We introduce auxiliary generators $f_1, f_2$ and $\{p_{1,j}\}_{j=1}^5$ such that they satisfy the linear relations:
\begin{align*}
    &f_0 f_1 f_2 = e && b_1 f_2 p_{1,1} = e && p_{1,1} p_{1,2} p_{1,3} = e\\
	&f_0 p_{1,3} p_{1,4} = e && c_1 p_{1,4} p_{1,5} = e \quad f_1 p_{1,2} p_{1,5} = e.
\end{align*}
Then, we expand $f_0b_1f_0$ by substituting in the equations above and
get
\begin{align*}
    f_0b_1f_0 = (f_1f_2)(f_2p_{1,1})(p_{1,3}p_{1,4}) =
    f_1 p_{1,2}p_{1,4} = p_{1,5}p_{1,4} = c_1.
\end{align*}
The other conjugacy relations of $\Pg_1$ are embedded in linear relations analogously.

A representation of $\Gamma$ can also be built from
a representation $\Psi_1$ of $\Pg_1 \circlearrowleft \mathbb{C}^2 \otimes \mathcal{H}$
that was constructed above. \carl{At this point the reader may be losing track of the precise meaning of what you're saying.  Perhaps you could simply say, ``A representation of $\Gamma$ can also be built from the
representation $\Psi_1 \circlearrowleft \mathbb{C}^2 \otimes \mathcal{H}$ that was constructed above.''}
\hfc{Fixed, but I worry about the symbol $\circlearrowleft$.}
We denote the representation of $\Gamma$ by $\Psi$ and
it is defined on $\C^2 \x \C^2 \x \calH$ such that
\begin{align*}
    \Psi(s) = \1_{\C^2} \x \Psi_1(s) \text{ for each }
    s \in S_1.
\end{align*}
In particular, it means that for each $a_i \in S_0$
\begin{align*}
    \Psi(a_i) = \1_{\C^2} \x \1_{\C^2} \x \Psi_0(a_i).
\end{align*}
Hence, a homomorphism $\phi: \Pg_1 \rightarrow \Gamma$ that 
maps $s$ to $s$ for each $s \in S_1$ is an embedding of $\Pg_1$ into $\Gamma$
by Lemma $15$ of Ref.~\cite{slofstra2017}.

%---------------------------------------------------
\subsection{Formal definitions}
\label{sec:gamma_def}
%---------------------------------------------------
We define the solution group of the linear system game $\LS(r)$ first, following the steps described in the previous subsection.
Then we define the game $\LS(r)$.
\begin{definition}
\label{def:gamma}
Define the set $S$ to be 
\begin{align*}
	S = \{a_i, b_i, c_i, d_i,\{ p_{i,j} \}_{j=1}^5\}_{i=1}^{r+5} \cup \{f_i,g_i,m_i\}_{i=0}^2 \cup \{h_{jk}\}_{(i,j,k) \in C(r)} \cup 
	\{\{q_{\bc,j} \}_{j=1}^6\}_{\bc \in C(r)},
\end{align*}
and the set $R$ to be the union of the following
set of linear relations:
\begin{itemize}
\item for each $i = 1 \dots r+5$:
\begin{align*}
	R_i =  \{ &a_i = b_ic_i = f_0d_i\quad
	%&g_2 a_i w_i = e \\
	f_0 f_1 f_2 = e \quad b_i f_2 p_{i,1} = e \quad p_{i,1} p_{i,2} p_{i,3} = e\\
	&f_0 p_{i,3} p_{i,4} = e \quad c_i p_{i,4} p_{i,5} =e \quad f_1 p_{i,2} p_{i,5} = e\},
\end{align*}
\item for each $ \bc = (i,j,k) \in C(r)$:
\begin{align*}
	R_{\bc} = \{&h_{jk}b_j c_k = e \quad
	d_i q_{\bc,1} f_2 = e \quad b_j f_2 q_{\bc,2} = e \quad q_{\bc,2} q_{\bc,3} q_{\bc,4} = e\\
	&d_i q_{\bc,4} q_{\bc,5} = e \quad c_k q_{\bc,5} q_{\bc,6} =e \quad q_{\bc,1} q_{\bc,3} q_{\bc,6} = e\},
\end{align*}
\item 
$
	R_{MS} = \{f_0 f_1 f_2 = e,\quad g_0 g_1 g_2 = e,\quad m_0 m_1 m_2 = e,\quad
	f_0 g_2 m_0 = e, \quad f_2 g_0 m_1 = e \quad f_1 g_1 m_2 = J\},
$
\item $R_J = \{ J s J s = e \vert s \in S\}$,
\item $R_{base} = \{ s^2 = e \vert s \in S\}$.
\end{itemize}
\hf{The group $\Gamma$ is a group with the presentation
$\ip{S \cup \{J\} : R}$.}
\end{definition}

From the group $\Gamma$ we can construct the binary linear system game $\LS(r)$. Basically,
we associate a variable $x(s)$ to each generator $s \in S$.
Then each linear relation in $R$ can be translated to a linear equation.
For example, the linear relation $f_0f_1f_2 = e$ is translated to the equation $x(f_0) + x(f_1) + x(f_2) = 0$, and the relation 
$f_1g_1m_2 = J$ is translated to the equation
$x(f_1) + x(g_1) + x(m_2) = 1$. 
The complete list of the equations is given in \cref{def:lsg_eq}.
\begin{definition}
\label{def:lsg}
The linear system game $\LS(r)$ consists of
\begin{align*}
    & \calX^{\LS} = \{I_i\}_{i=1}^{\mr}, \\
    & \calY^{\LS} = \{ x(s) : s \in S \},
\end{align*}
where $I_i = \{ s : H(i,s) = 1\}$ is the set of all the nonzero coefficient of equation $i$
and $\mr := 14r + 62$ is the number of equations.  
\carl{Since you are defining Alice's inputs to be subsets of S, why don't you just define Bob's inputs to be elements of S? Also, again you need to account that
$J$ is an element of $S$.}
\hfc{I think setting $\calY = S$ will cause confusion.
You can see the forms of the equations in \cref{def:lsg_eq}.
If I set the question set to be $S$, the reader will confuse the 
linear equations with linear relation.
I have moved $J$ out of $S$.}
Details of $I_i$ for $1 \leq i \leq \mr$ can be found in \cref{def:lsg_eq}.
The answer sets are 
\begin{align*}
    \calA^{\LS} = (\Z_2)^{I_i} && \calB^{\LS} = \Z_2,
\end{align*}
because $|I_i| = 3$ for all $i$.
The probability distribution is uniform over all the pairs $(I_i, x(s))$ such that $s \in I_i$, so
\begin{align*}
    \pi^{\LS}(I_i, x(s)) = 
    \begin{cases}
        1/N(r) & \text{ if } s \in I_i \\
        0 & \text{otherwise,}
    \end{cases}
\end{align*}
where $N(r) := 157r + 685$ is the total number of valid question pairs.
We define $X_i := \{ \ba \in (\Z_2)^{I_i}: \sum_{s \in I_i} a(s) = c(i) \}$, which is the set of all the valid answers of equation $i$.
Given an answer $(\ba,b)$ for question $(I_i,x(s))$, 
the score function is
\begin{align*}
    V^{\LS}_{I_i, x(s)}(\ba, b) = 
    \begin{cases}
        1 \text{, if } \ba \in X_i \text{ and } a(s) = b\\
        0 \text{, otherwise}.
    \end{cases}
\end{align*}
\end{definition}
\carl{This definition does not seem consistent.  You are using $a$ both as a function on $\{ 1, 2, 3 \}$ and as a function on $S$.}
\hfc{Fixed.}
The construction of $\LS(r)$ proves the following theorem.
\begin{theorem}
	The group $\Pg$ can be embedded in the solution group of a binary linear system game which has
	$\nr := 16r+75$ variables and $\mr := 14r + 62$ equations, where each equation has $3$ variables.
\end{theorem}
\hf{Note that when $\LS(r)$ is played between Alice and Bob, the total
number of equation and variable pairs is $N(r)$ is of order $\Theta(r)$.}

>>>>

The inspiration comes from 
Slofstra's seminal work~\cite{slofstra2017}, in which he
embeds a group with generators $x$ and $y$ satisfying the relation $xyx^{-1}=y^2$
into the solution group of a binary linear system game.  
We generalize the relation $xyx^{-1} = y^2$ and embed the 
following group
\begin{align}
    \Pg = \ip{u,o:uou^{-1} = o^r},
\label{eq:pgroup}
\end{align}
for some $r \in \N$ into the solution group, denoted by $\Gamma$, of a binary linear system game, denoted by $\LS(r)$.
The steps to embed $\Pg$ into $\Gamma$ follows the procedure detailed 
in the proofs of Proposition~$33$, Lemma~$29$ and Proposition $27$ of Ref.~\cite{slofstra2017}, 
so the group $\Pg$ (\cref{eq:pgroup}) is first embedded into $\Pg_0$ (\cref{def:g0}), then $\Pg_1$ (\cref{def:g1}), and finally into the group $\Gamma$ (\cref{def:gamma}),
and we obtain a chain of embeddings:
\begin{align}
\Pg \hookrightarrow \Pg_0 \hookrightarrow \Pg_1 \hookrightarrow \Gamma.
\end{align}

This section is structured as follows.
In \cref{sec:g0}, we define the group $\Pg_0$ and prove that $\Pg$ is embedded in $\Pg_0$.
In \cref{sec:g1}, we define the group $\Pg_1$ and prove that $\Pg_0$ is embedded in $\Pg_1$.
\Cref{sec:gamma} contains the definition of the group $\Gamma$ and the proof that $\Pg_1$
is embedded in $\Gamma$.
The purposes of introducing each intermediate
group are explained along the definition.
Note that, we defer the full definitions of the representations of $\Pg_0$, $\Pg_1$ and $\Gamma$
until \cref{sec:rep_gamma}. 
Instead, We only highlight a few operators from a finite-dimensional representation of $\Gamma$.
The representation will be used later to build the ideal strategy.
In \cref{sec:gamma_def}, we construct $\LS(r)$ from $\Gamma$ and give the 
formal definition of $\LS( r )$.

%----------------------------------------
\subsection{The group $\Pg_0$}
\label{sec:g0}
%----------------------------------------

The group $\Pg_0$ is a conjugacy group (\cref{def:spe_conj_grp}), and is defined below.
The purpose of this step is to embed $\Pg$ into a group where all the
generators are of order-$2$, because
it is impossible to find a homomorphism from $\Pg$ to a solution group that maps $u$ or $o$, which can have arbitrary order, to a single generator. On the other hand, 
a homomorphism from $\Pg_0$ to a solution group can be easier to find.
\begin{definition}	
\label{def:g0}
	Let the set $S_0$ be 
	\begin{align*}
		S_0 = \{o_i\}_{i=1}^{r} \cup \{u_i\}_{i=1}^5,
	\end{align*}
	and the set $R_0$ be the union of 
	\begin{align*}
	&R_{base} = \{s^2 = e | s \in S\},\\
	&R_{u} = \{ u_3 = u_2o_1u_2 \quad u_4 = u_2o_2u_2 \quad 
	u_5 = u_1u_3u_1 \quad o_2 = u_1u_4u_1 \quad u_5 = o_1 o_r o_1\},
	\end{align*}
	and 
	\begin{align*}
	R_o = 
	\begin{cases} 
	\bigcup_{j=1}^{r/2-1}\{ o_{1+2j} = o_1o_{2j}o_1 \quad o_{2+2j} = o_2o_{1+2j}o_2\} \quad \text{ if $r$ is even },\\
	\{o_3 = o_2o_1o_2\} \cup \bigcup_{j=1}^{(r-3)/2}\{
	 o_{2+2j} =o_1o_{1+2j}o_1 \quad o_{3+2j} = o_2o_{2j+2}o_2 \}\quad\text{ if $r$ is odd }.
	\end{cases}
	\end{align*}
	The group $\Pg_0$ is a group with presentation $\ip{R_0:S_0}$.
\end{definition}
The special generators of $\Pg_0$ are $o_1, o_2, u_1$ and $u_2$ because the product $o_1o_2$ behaves similarly as $o$
and the product $u_1u_2$ behaves similarly as $u$.
Moreover, the conjugacy relations in $R_0$ can be combined to recover the relation $uou^{-1} = o^r$,
as proved in the next proposition.
\begin{proposition}
    \label{prop:g0}
	The group $\Pg$ is embedded in $\Pg_0$.
	Furthermore, the generators of $\Pg_0$ satisfy the relation 
	\begin{align}
	    \label{eq:uo_comm}
	    &(u_1u_2) o_2 (u_2u_1) = o_2 \\ 
	    \label{eq:uo_rel}
		&(u_1u_2)^j o_1o_2 (u_2u_1)^j = (o_1o_2)^{r^j}, 
	\end{align}
	for any $ j \in \N$.
\end{proposition}
\begin{proof}
    We prove \cref{eq:uo_comm} first. It is easy to see that
    \begin{align}
        u_1 (u_2o_2u_2) u_1 = u_1u_4u_1 =o_2.
    \end{align}

    Next, we prove that $\Pg$ is embedded in $\Pg_0$ by prove the $j = 1$ case of \cref{eq:uo_rel}.
    The proof of Proposition $33$ of Ref.~\cite{slofstra2017} gives the recipe about
    how to construct a finite-dimensional representation of $\Pg_0$ from a 
    finite-dimensional representation of $\Pg$, so Lemma $15$ of Ref.~\cite{slofstra2017}
    proves that a homomorphism $\phi: \Pg \rightarrow \Pg_0$ such that $\phi(u) = u_1u_2$ and 
    $\phi(o) = o_1o_2$ is injective.

	Now assume the statement is true for $j = n$, then for $j = n+1$
	\begin{align*}
		(u_1u_2)^{n+1} o_1o_2 (u_2u_1)^{n+1} =& u_1u_2 (o_1o_2)^{r^n} u_2u_1 \\ 
		 =& (u_1u_2 o_1o_2 u_2u_1)^{r^n} \\
		 =& (o_1o_2)^{r^{n+1}},
	\end{align*}
	where from the first line to the second line, we insert $(u_2u_1)(u_1u_2)$ between every pair of $o_1o_2$, and
	from the second line to the third line, we applied the $j=1$ case. Hence, the statement is true.
\end{proof}
Note that our representation $\Psi_0$ of $\Pg_0$ is different from the representation
constructed in the proof of Proposition $33$ of Ref.~\cite{slofstra2017}.
We give the formal definition of $\Psi_0$ (\cref{def:rep_g0}) in \cref{sec:rep_gamma}.

To better characterize all the conjugacy
relations of $\Pg_0$ and simplify the form of $\Pg_0$, 
we relabel $u_i$ and $o_i$'s as $a_i$'s such that
\begin{align}
	a_j := 
	\begin{cases}
	 o_j \text{ for } j = 1,2 \\
	 u_{j-2} \text{ for } j = 3\dots 7 \\
	 o_{j-5} \text{ for } j = 8 \dots r+5.
	\end{cases}
\end{align}
Then we define the set $C(r)$ of tuples $(i,j,k)$ such that
\begin{align}
\label{eq:cr}
	C(r) = \{ (i,j,k) |  (a_ia_ja_i = a_k) \in R_0 \}.
\end{align}
The size of $C(r)$ is $r+3$. 
Hence, another presentation of the group $\Pg_0$ is
\begin{align*}
    \Pg_0 = \ip{ \{a_i\}_{i=1}^{r+5} : \{a_i^2 =e \}_{i=1}^{r+5} \cup \{ a_ia_ja_i = a_k \vert (i,j,k) \in C(r)\}},
\end{align*}
and we will construct $\Pg_1$ based on this presentation of $\Pg_0$.

%---------------------------------
\subsection{The group $\Pg_1$}
\label{sec:g1}
%---------------------------------
The group $\Pg_1$ is a nice conjugacy group (\cref{def:nice_conj_grp}).
We embed $\Pg_0$ into $\Pg_1$ to
make the construction of a finite-dimension representation of $\Gamma$ from
a finite-dimension representation of $\Pg_1$ easier.
\begin{definition}
\label{def:g1}
Define the set $S_1$ to be
\begin{align*}
	S_1 = \{a_i, b_i, c_i, d_i\}_{i=1}^{r+5} \cup \{ f_0 \} \cup \{h_{jk}\}_{(i,j,k) \in C(r)},
\end{align*}
and the set $R_1$ to be
\begin{align*}
	R_1 = &\{ s^2 = e \vert s \in S_1\}\\ 
	&\cup 
	\{a_i = b_ic_i = f_0d_i, \quad f_0b_if_0 =c_i\}_{i= 1}^{r+5} \\ 
	&\cup
	\{h_{jk}b_j c_k = e, \quad d_ib_jd_i = c_k\}_{(i,j,k) \in C(r)}.
\end{align*}
The group $\Pg_1$ is a group with the presentation $\ip{S_1 : R_1}$.
\end{definition}
Note that the group $\Pg_1$ is the same as the group $K$ used in the proof of Lemma $29$ of Ref.~\cite{slofstra2017}.
For each $1 \leq i \leq r+5$, the relation $a_i = b_ic_i$ guarantees that $b_i$ commutes with $c_i$.
For each $(i,j,k) \in C(r)$, the linear relation $h_{jk} b_j c_k = e$ guarantees that
$b_j$ commutes with $c_k$.

The relation between $\Pg_0$ and $\Pg_1$ is summarized in the propositions below, which 
is a specific case of Lemma $29$ of \cite{slofstra2017}.
\begin{proposition}
    \label{prop:g0g1}
	The group $\Pg_0$ is embedded in $\Pg_1$. 
\end{proposition}
\begin{proof}
    We prove this proposition by showing that generators $a_i$'s in $S_1$
    satisfy the relation $a_i a_j a_i = a_k$ for all $(i,j,k) \in C(r)$.
    This means the homomorphism $\phi: \Pg_0 \rightarrow \Pg_1$ that maps $a_i$
    to $a_i$ is homomorphism from $\Pg_0$ to $\Pg_1$.

	We first show that $d_i c_j d_i = b_k$, which is because
	\begin{align*}
		d_i c_j d_i = d_i (f_0 b_j f_0) d_i = f_0 (d_i b_j d_i) f_0 = f_0 c_k f_0 = b_k.
	\end{align*}
	Then, we can prove that 
	\begin{align*}
		a_i a_j a_i = f_0 d_i b_j c_j f_0 d_i 
		= (f_0 d_i b_j d_i f_0)(f_0 d_i c_j d_i f_0) 
		= (f_0 c_k f_0)(f_0 b_k f_0) 
		= b_k c_k = a_k,
	\end{align*}
	where we use the fact that $f_0$ commutes with $d_i$.

	A representation of $\Pg_1$ can also be built upon a representation of $\Pg_0$.
    Suppose $\Psi_0$ is a representation of $\Pg_0$ on some Hilbert space $\calH$, then 
    a representation of $\Pg_1$, $\Psi_1$, on the Hilbert space $\C^2 \x \calH$ can
    be constructed such that
    \begin{align*}
        &\Psi_1(a_i) = \1_{\C^2} \x \Psi_0(a_i)
    \end{align*}
    as proved in Lemma $29$ of Ref.~\cite{slofstra2017}.
    Then, the injectivity of $\phi$ follows Lemma $15$ of Ref.~\cite{slofstra2017}.
\end{proof}
The consequence of this proposition is that $\Pg$ can be embedded in $\Pg_1$.
We give the formal definition of the represention $\Psi_1$ of $\Pg_1$ 
(\cref{def:rep_g1}) in \cref{sec:rep_gamma}.

%-------------------------------------
\subsection{The group $\Gamma$}
\label{sec:gamma}
%-------------------------------------
The group $\Gamma$ is a solution group,
so all the generators of $\Gamma$ are of order-$2$
and all the relations are linear relations.
Moreover, the linear relations can be combined
to recover the conjugacy relations in $R_1$.
\begin{definition}
\label{def:gamma}
Define the set $S$ to be 
\begin{align*}
	S = \{a_i, b_i, c_i, d_i,\{ p_{i,j} \}_{j=1}^5\}_{i=1}^{r+5} \cup \{f_i,g_i,m_i\}_{i=0}^2 \cup \{h_{jk}\}_{(i,j,k) \in C(r)} \cup 
	\{\{q_{\bc,j} \}_{j=1}^6\}_{\bc \in C(r)},
\end{align*}
and the set $R$ to be the union of the following
set of linear relations:
\begin{itemize}
\item for each $i = 1 \dots r+5$:
\begin{align*}
	R_i =  \{ &a_i = b_ic_i = f_0d_i\quad
	%&g_2 a_i w_i = e \\
	f_0 f_1 f_2 = e \quad b_i f_2 p_{i,1} = e \quad p_{i,1} p_{i,2} p_{i,3} = e\\
	&f_0 p_{i,3} p_{i,4} = e \quad c_i p_{i,4} p_{i,5} =e \quad f_1 p_{i,2} p_{i,5} = e\},
\end{align*}
\item for each $ \bc = (i,j,k) \in C(r)$:
\begin{align*}
	R_{\bc} = \{&h_{jk}b_j c_k = e \quad
	d_i q_{\bc,1} f_2 = e \quad b_j f_2 q_{\bc,2} = e \quad q_{\bc,2} q_{\bc,3} q_{\bc,4} = e\\
	&d_i q_{\bc,4} q_{\bc,5} = e \quad c_k q_{\bc,5} q_{\bc,6} =e \quad q_{\bc,1} q_{\bc,3} q_{\bc,6} = e\},
\end{align*}
\item 
$
	R_{MS} = \{f_0 f_1 f_2 = e,\quad g_0 g_1 g_2 = e,\quad m_0 m_1 m_2 = e,\quad
	f_0 g_2 m_0 = e, \quad f_2 g_0 m_1 = e \quad f_1 g_1 m_2 = J\},
$
\item $R_J = \{ J s J s = e \vert s \in S\}$,
\item $R_{base} = \{ s^2 = e \vert s \in S\}$.
\end{itemize}
\hf{The group $\Gamma$ is a group with the presentation
$\ip{S \cup \{J\} : R}$.}
\end{definition}

In the next proposition, we prove that the group $\Pg_1$ is embedded in $\Gamma$.
\begin{proposition}
    \label{prop:g1gamma}
	The group $\Pg_1$ can be embedded in $\Gamma$.
	The generators of $\Gamma$ also satisfy the relations: 
	\begin{align}
	    \label{eq:mg1} &f_0 g_0 f_0 g_0 = J,\\
	    \label{eq:mg2} &f_2 g_2 f_2 g_2 = J.
	\end{align}
\end{proposition}
\begin{proof}
    To prove the first claim, we show that the generators
    $b_i$, $c_i$, $d_i$ satisfy the relations
    $d_ib_jd_i = c_k$ for each $\bc = (i,j,k) \in C(r)$.
    \begin{align*}
        d_ib_jd_i =& (k_{\bc 1} f_2)(f_2 k_{\bc 2})(k_{\bc 4} k_{\bc 5})\\ 
        =& k_{\bc 1}(k_{\bc 2}k_{\bc 4})k_{\bc 5} \\
        =& (k_{\bc 1} k_{\bc 3}) k_{\bc 5} \\
        =& k_{\bc 6} k_{\bc 5} \\
        =& c_k.
    \end{align*}
    The derivation of $f_0 b_i f_0 = c_i$ is similar for $1 \leq i \leq r+5$, so we omit it here.
    Hence, a map $\phi:\Pg_1 \rightarrow \Gamma$ that maps $s$
    to $s$ for each $s \in S_1$ is a homomorphism between $Pg_1$ and 
    $Gamma$. 
    A representation of $\Gamma$ can be constructed from a representation 
    of $\Pg_1$ as shown in the proof of Proposition $27$ of Ref.~\cite{slofstra2017},
    so Lemma $15$ of Ref.~\cite{slofstra2017} proves the homomorphism $\phi$
    is injective.

    The second claim follows a similar derivation
    using linear relations in $R_{MS}$, so we omit it here.
\end{proof}
Since $\Pg$ is embedded in $\Pg_1$, we can conclude that
$\Pg$ is embedded in $\Gamma$ as well.

The representation $\Psi$ of $\Gamma$ is defined on the Hilbert space
$W_2 \x W_2 \x W_{d-1}$,
where $W_k$ denotes a Hilbert space of
dimension $k$. 
The formal definition of $\Gamma$ is defined in \cref{def:rep_gamma}
in \cref{sec:rep_gamma}.
We denote the
standard basis of $W_k$ by $\{\ket{x_j}\}_{j=1}^{k}$.
We define an operator $O$ on $W_{d-1}$ as
\begin{align*}
    O = \sum_{j=1}^{d-1} \omega_d^j \ketbra{x_j}{x_j}.
\end{align*}
Note that another form of the basis of $W_{d-1}$ is $\{\ket{x_{r^j}}\}_{j=0}^{d-2}$, 
where the subscript $r^j$ is taken modulo $d$ implicitly,
because another form of $O$ is 
\begin{align}
    \label{eq:O}
    O = \sum_{j=0}^{d-2} \omega_d^{r^j} \ketbra{x_{r^j}}{x_{r^j}}.
\end{align}
We use the second form of the basis when it is convenient.
The other basis of $W_{d-1}$ that we use is $\{ \ket{u_j} \}_{j=0}^{d-2}$ given by
\begin{align*}
	\ket{u_k} = \frac{1}{\sqrt{d-1}} \sum_{j=0}^{d-2} \omega_{d-1}^{jk} \ket{x_{r^j}}.
\end{align*}
We denote the identity operator for the subspace $W_k$ by $\1_{W_k}$.
The representations of $a_1, a_2, a_3$ and $a_4$ are 
\begin{align}
    \label{eq:o1} \Psi(a_1) &= \1_{W_2} \x \1_{W_2} \x \left(\sum_{j=1}^{(d-1)/2} \omega_d^j \ketbra{x_j}{x_{d-j}} + \omega_d^{-j} \ketbra{x_{d-j}}{x_{j}}\right) \\
    \label{eq:o2} \Psi(a_2) &= \1_{W_2} \x \1_{W_2} \x \left(\sum_{j=1}^{d-1} \ketbra{x_j}{x_{d-j}} \right).
\end{align}
\begin{equation}
    \begin{aligned}
    \label{eq:u1} \Psi(a_3) &= \1_{W_2} \x \1_{W_2} \x \Big[\ketbra{u_0}{u_0} +\omega_{d-1}^{(d-1)/2}\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}}\\ 
    &+ \sum_{k=1}^{(d-3)/2}\left( \omega_{d-1}^k\ketbra{u_k}{u_{d-1-k}} + \omega_{d-1}^{-k}\ketbra{x_{d-1-k}}{x_k}\right) \Big]
    \end{aligned}
\end{equation}
\begin{equation}
    \begin{aligned}
    \label{eq:u2}\Psi(a_4) &= \1_{W_2} \x \1_{W_2} \x \Big[\ketbra{u_0}{u_0} +\ketbra{u_{(d-1)/2}}{u_{(d-1)/2}} \\
	& + \sum_{k=1}^{(d-3)/2}\left(\ketbra{u_{d-1-k}}{u_k} + \ketbra{u_k}{u_{d-1-k}}\right)\Big].
    \end{aligned}
\end{equation}

% A representation of $\Gamma$ can also be built from
% a representation $\Psi_1$ of $\Pg_1 \circlearrowleft \mathbb{C}^2 \otimes \mathcal{H}$
% that was constructed above.
% We denote the representation of $\Gamma$ by $\Psi$ and
% it is defined on $\C^2 \x \C^2 \x \calH$ such that
% \begin{align*}
%     \Psi(s) = \1_{\C^2} \x \Psi_1(s) \text{ for each }
%     s \in S_1.
% \end{align*}
% In particular, it means that for each $a_i \in S_0$
% \begin{align*}
%     \Psi(a_i) = \1_{\C^2} \x \1_{\C^2} \x \Psi_0(a_i).
% \end{align*}
% Hence, a homomorphism $\phi: \Pg_1 \rightarrow \Gamma$ that 
% maps $s$ to $s$ for each $s \in S_1$ is an embedding of $\Pg_1$ into $\Gamma$
% by Lemma $15$ of Ref.~\cite{slofstra2017}.

%---------------------------------------------------
\subsection{Formal definitions}
\label{sec:gamma_def}
%---------------------------------------------------
We define the solution group of the linear system game $\LS(r)$ first, following the steps described in the previous subsection.
Then we define the game $\LS(r)$.
